Trauma treatment delay

### 2023-12-05 manuscriptlongversion.Rmd
text

Key results

@@

@@

The problem mentioned above with too few patients in the outcome group
made this into a post hoc analysis. As we didn't know the amount of
people who received delayed treatment when we handled the scrambled
data, we ran the code on the real data when we had too many variables
for the dataset. Therefore, we had to change the variables after having
seen the real data, making it a post hoc analysis. This could in theory
open up for possible selection bias, as we might choose variables which
give us results we are looking for. However, all the variables included
in the final analysis were already included in the first one. Variables
were only removed, not added after having seen the real data.

@@

>>>>

@@

Respiratory rate also had the correlation that lower respiratory rate
correlated with lower rates of delayed treatment among the patients.

Number of injuries was significant when unadjusted, but the correlation
dissapeared when adjusted for with other variables. Our guess as to why
this is due to confounding due to it's shared variability with the ISS
variable. Number of injuries and ISS is often correlated as a more
severely injured patient will both score higher on ISS and number of
injuries. Therefore, we hypothesize that the effect of number of
injuries become insignificant when adjusting for ISS.

@@

The problem mentioned above with too few patients in the outcome group
made this into a post hoc analysis. As we didn't know the amount of
people who received delayed treatment when we handled the scrambled
data, we ran the code on the real data when we had too many variables
for the dataset. Therefore, we had to change the variables after having
seen the real data, making it a post hoc analysis. This could in theory
open up for possible selection bias, as we might choose variables which
give us results we are looking for. However, all the variables included
in the final analysis were already included in the first one. Variables
were only removed, not added after having seen the real data. The best
way to have gone about this would have been to just look at the amount
of people who received delayed treatment before choosing the variables.
Then, choosing an amount of variables that would work with the amount of
patients. This would have avoided making it post hoc and changing the
variables after seeing the data.

@@

Another limitation with this study is that logistical regressions
assumes that the data is binomial, which the data used is not. The
analysis assumes a linear correlation between the dependent variable and
the independent variable, which is best analysed in a normal
distribution.
